Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-07-02 paper.tex
Rearrange figures now that they are force placed H

\subsection{Idealized Compact Star:
  Testing Gravitational Redshift and Geodesic Curvature}
\label{ssec:test_gravity}
Optically thick star in Schwarszchild.
\todo{describe $L(r)$, as a function of lapse}
optically thick disk in Kerr (Fishbone-Moncrief disk):
set up to give two different surfaces for nue vs nua, but same temp (?).
\todo{plot of analytic and numerical geodesics}
\todo{plot of $G$ nue vs nua}

>>>>

\subsection{Idealized Compact Star:
  Testing Gravitational Redshift and Geodesic Curvature}
\label{ssec:test_gravity}
Optically thick star in Schwarszchild.
Total luminosity at infinite separation may be computed by
computing the radial energy flux at a finite separation from the star, $r$,
and using $p_t$ for the energy. We compute this asymptotic luminosity
at several radii, $r$, and show that the luminosity is independent of
the observer's radius.
\todo{compute $L$, put in figure}
